---
title: "R Notebook"
output: html_notebook
---

```{r}
data(anscombe)
str(anscombe)
```
```{r}
var(anscombe)
```
```{r}
attach(anscombe)
```

```{r}
sapply(anscombe, FUN = mean)
```
```{r}
sapply(anscombe, FUN = var)
```
± Similarity of the 8 datasets on basis of mean() and var() :x and y values are same in each function output.

±Boxplots of 8 datasets:
```{r}
boxplot(x1, horizontal = TRUE)
```
```{r}
boxplot(x2, horizontal = TRUE)
```

box

```{r}
boxplot(x3, horizontal = TRUE)
```
```{r}
boxplot(x3, horizontal = TRUE)
```
```{r}
boxplot(x4, horizontal = TRUE)
```
```{r}
boxplot(y1, horizontal = TRUE)
```
```{r}
boxplot(y2, horizontal = TRUE)
```
```{r}
boxplot(y3, horizontal = TRUE)
```
```{r}
boxplot(y4, horizontal = TRUE)
```
```{r}
sapply(anscombe, FUN = IQR)

```

```{r}
library(e1071)
sapply(anscombe, FUN = skewness)
```
±Plot:
```{r}
?plot()
```

±Using plot function/cor:
```{r}
library(tidyverse)

x <- anscombe[ ,1:4]
y <- anscombe[ ,5:8]

cor(x,y)
```
```{r}
diag( cor(x,y))
```
```{r}
ggplot(data=anscombe, mapping=aes(x=x1, y=y1)) +
  geom_point() +
  labs(title="Pair 1") +
  stat_smooth(method="lm", se= FALSE)
  
  

```
```{r}
ggplot(data=anscombe, mapping=aes(x=x2, y=y2)) +
  geom_point() +
  labs(title="Pair 2") +
  stat_smooth(method="lm", se= FALSE)
```
```{r}
ggplot(data=anscombe, mapping=aes(x=x3, y=y3)) +
  geom_point() +
  labs(title="Pair 3") +
  stat_smooth(method="lm", se= FALSE)
```
```{r}
ggplot(data=anscombe, mapping=aes(x=x4, y=y4)) +
  geom_point() +
  labs(title="Pair 4") +
  stat_smooth(method="lm", se= FALSE)
```

±Findings:
1. Similarity of 8 datasets on basis of mean() and var(): appear similar however, no conclusions can be drawn in terms of the relationship between the pairs (i.e. x1, y1 etc.)  

2. Boxplots: looking at each value in a separate graph shows further detial - an outlier in x4;  
variance - y4 is left skewed , y3 qnd y4 are right skewed.

3. Interpreting the 8 datasets as four sets of (x,y) data: the 4 sets deliver the same positive correlation (0.8) even though the relationships between each pair in the scatter graphs are different.



