---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
data(msleep)
```
```{r}
glimpse(msleep)

tail(msleep)
view(msleep)
```
Jabberwockies sleep for around 7 hours a night, on average. Perform an appropriate statistical test to determine whether the mean sleep_total in the sampled population of animal types differs from the typical value for jabberwockies.

```{r}

mean_now <- mean(msleep$sleep_total)
mean_now

t.test(x = msleep$sleep_total, mu = 7, alternative = "less")
```
```{r}
#Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

carnv <- msleep %>%
 filter(msleep$vore == "carni")

herbv <- msleep %>%
  filter(msleep$vore =="herbi")
  
t.test(x = carnv$sleep_total, y = herbv$sleep_total, alternative = "less", paired = FALSE)

```
Perform an appropriate statistical test to determine whether the proportion of domesticated animals in the population of animal types is greater than 5%.

```{r}
num_domesticated_aniamals <- msleep %>%
  filter(conservation == "domesticated") %>%
  count()
num_domesticated_aniamals

```
```{r}
prop.test(x = num_domesticated_aniamals$n, n = nrow(msleep), p = 0.05, alternative = "two.sided", correct = TRUE)
```
```{r}
0.05 * nrow(msleep) >= 10
```

Determine an appropriate sample size for the following problem:
A quality analyst wants to estimate a 99% confidence interval to within ±0.01g for the mean weight of fruit pastels produced by a production line tomorrow. Prior evidence suggests the standard deviation in fruit pastel weights is 0.05g. What is the minimum number of fruit pastels the analyst should sample?
```{r}
#correct quartile for 99% CI = 0.995 - 0.005 off each side 
sd_popn <- 0.05
PME = 0.01
n <- qnorm(0.995)^2 * 0.05^2 / 0.01^2
n
```

Determine an appropriate sample size for the following problem:

A clinical dietician wants to compare two different diets, A and B, for diabetic patients. She hypothesizes that diet A (Group 1) will be different from diet B (Group 2), in terms of mean blood glucose. She plans to get a random sample of diabetic patients and randomly assign them to one of the two diets. At the end of the experiment, which lasts 6 weeks, a fasting blood glucose test will be conducted on each patient. She also expects that the average difference in blood glucose measure between the two group will be about 10 mg/dl. Furthermore, she also assumes the standard deviation of blood glucose distribution for diet A to be 15 mg/dl and the standard deviation for diet B to be 17 mg/dl. The dietician wants to know the number of subjects needed in each group assuming equal sized groups.


What would the power of the test above be if the number of patients in each group was 100?

```{r}
library(WebPower)

```

```{r}
effect_size <- 15 /17
effect_size

wp.t(n1 = NULL, d = effect_size, alpha = 0.05, power = 0.95, type = "paired", alternative = "two.sided")
```
```{r}
Will need 19 patients minimum in each group
```

