---
title: "R Notebook"
output: html_notebook
---


```{r}
library(readr)
library(ggplot2)
library(tidyverse)

project_management <- read_csv("project_management.csv")

project_management

```

```{r}
project_management_model <- lm(formula = actual_length ~ estimated_length, data = project_management)

project_management_model
```

```{r}
fitted(object = project_management_model)
```

```{r}


```
```{r}
plot(project_management$estimated_length, project_management$actual_length)

predict_at <- data.frame(estimated_length = seq(0, 30, 1))
predicted_y <- predict(object = project_management_model, newdata  = predict_at)

lines(predict_at$estimated_length, predicted_y)  
  
```
OUTLIER: estimated_length 22, actual_length 39

```{r}
plot(predict(project_management_model), resid(project_management_model))
abline(0, 0)
lines(loess.smooth(predict(project_management_model), resid(project_management_model)), lwd = 2, col = "red")
```

```{r}
plot(predict(project_management_model), resid(project_management_model))
abline(0, 0)
```
```{r}
plot(project_management_model)
```
FINDINGS
 - weak neagative correlation between estimated_length and actual_length 
  - plot shows majoirty of data points are within the dashed Cook's distance line apart from point 50 (outlier) with a very different value from that predicted by the regression model) which appears to be influential and would warrant further evaluation.  



